---
title: "R operators"
output:
  html_document:
    df_print: paged
---
**Attribution operators**

= or <-

```{r}
ex1 <- 4
ex1
ex2 = 4
ex2
```


**Math Operators**

Addtion (+)

```{r}
1+1 
```

Subtraction (-)

```{r}
1-1
```

Multiplication (*)

```{r}
1*4
```

Division (/)

```{r}
6/3
```

Exponentiation (^)

```{r}
2^4
```
Square root (sqrt)*

```{r}
sqrt(9)
```
* Note that to compute the square root we use a function, not an operator(we will understand the difference in future)

Modulus (%%)

```{r}
10%%3
```

Integer division (%/%)

```{r}
10%/%3
```

**Logical Operators**


Less than (<)

```{r}
3 < 4
10 < 6
10 < 10
```

Less or equal to (<=)

```{r}
3 <= 4
10 <= 6
10 <=10
```

Greater than (>)

```{r}
3 > 4
10 > 6
10 > 10
```

Greater or equal to (>=)

```{r}
3 >= 4
10 >= 6
10 >= 10
```

Equal to (==)*

```{r}
2 == 3
2 == 2
```
* Note there's a difference between Equal operator (==) and attribution operator (=). This a common mistake!

Not, negation operator (!)

```{r}
3 < 4 
! 3 < 4
2 == 2
2 != 2
```

And (&)

```{r}
3 < 4 & 4 > -1
23 == 46/2 & 43 - 4 == 12*5
```

Or (|)

```{r}
3 < 4 | 4 > 5
23 == 46/2 | 43 - 4 == 12*5
```